---
title: "IPL"
author: "Ganesh"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---
<h1 style="text-align:center; color:Green; font-size:36px; font-family:Arial, sans-serif;">**INDIAN PREMIER LEAGUE**</h1>


<h2 style="color:Navy; font-size:30px; font-family:Georgia, sans-serif;">**Information**</h2>

- Indian Premier League consists of a total of 10 teams.
- The team names are mentioned below:
  - Chennai Super Kings
  - Mumbai Indians
  - Royal Challengers Bangalore
  - Sunrisers Hyderabad
  - Rajasthan Royals
  - Delhi Capitals
  - Kolkata Knight Riders
  - Kings XI Punjab
  - Lucknow Super Giants
  - Gujarat Titans
- IPL has completed successfully 15 years and is currently in its 16th edition.

<h2 style="color:Navy; font-size:30px; font-family:Georgia, sans-serif;">**Some Things To Remember in IPL**</h2>

- Compared to all the teams, there is a huge fanbase for Chennai Super Kings, Mumbai Indians, and Royal Challengers Bangalore.
- The team which appeared more times in the playoffs is Chennai Super Kings (CSK).
- The team which won more times the IPL trophy is Mumbai Indians (MI) which is 5 times.
- The team which set the record for the highest score is Royal Challengers Bangalore (RCB).
- The team which set the record for the lowest score is Royal Challengers Bangalore (RCB).
- The highest individual score in an IPL  by a player named "Chris Gayle" from Royal Challengers Bangalore (RCB).

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


## **Table View of the IPL winners List**
```{r , echo = FALSE,warning=FALSE}
require(knitr)
data <- read.csv("C://Users//FL_LPT-194//Documents//R//Download_button_Task//IPL_winners.csv")
kable(data)

```

## **Graphical Representation  of the above dataset**
```{r , echo = FALSE,warning=FALSE}
require(ggplot2)
ggplot(data, aes(x = YEAR, y = WINNERS)) +
  geom_point(size = 2) +
  labs(x = "Year", y = "Winners") +
  ggtitle("IPL Winners Scatter Plot")


```






